Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-10 docs/ms.tex
Update ms.tex

Suppose we know the ellipticity distribution of unlensed galaxies
based on some parasmeters $\alpha$, then we can write the likelihood
of reduced shear and $\alpha$:

>>>>

Suppose we know the ellipticity distribution of unlensed galaxies
based on some parasmeters $\alpha$, then we can write down the likelihood
of reduced shear and $\alpha$:
